---
title: "Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(alethiaR)
```

## Match against a reference list

The default matches on spelling and needs no model.

```{r}
messy <- c("New Yrok", "Los Angelos", "Chicagoo", "Houston")
reference <- c("New York", "Los Angeles", "Chicago", "Houston", "Phoenix")

alethia(messy, reference)
```

## Match on meaning

`as_embedder()` takes any function returning one row per string, so no download is
needed to see the embedding path work. A character-count embedder stands in for a
real model here.

```{r}
char_bag <- function(x) {
  t(vapply(strsplit(tolower(x), ""), function(ch) {
    tabulate(match(ch, c(letters, " ")), 27)
  }, numeric(27)))
}

match_by_embeddings(messy, reference, char_bag)
```

Pass a model name instead once an ONNX backend is registered; see
`?set_embedding_backend`.

## Choose a model without labels

`assess_models()` scores candidates on your own data. The composite is relative,
so it needs at least two.

```{r}
reversed <- function(x) {
  char_bag(vapply(strsplit(x, ""), function(ch) paste(rev(ch), collapse = ""), ""))
}

res <- assess_models(messy, reference, list(char_bag = char_bag, reversed = reversed))
res$table[, c("model", "score", "mean_margin_z", "mutual_nn_rate")]
```

```{r}
res$best
```

## Cluster without a reference list

Edges need mutual nearest-neighbour agreement, and each carries a confidence.

```{r}
entities <- c("Bombay", "Bombay City", "Calcutta", "Calcutta City", "Madras")
clusters <- cluster_entities(entities, char_bag, floor = 0.9)

clusters$clusters
```

```{r}
clusters$edges
```
